---
title: Barplots
author: Katie Reisinger
date: '2017-10-18'
slug: barplots
categories:
  - data visualization
  - ploting data
  - R
tags:
  - R Markdown
  - plot
---

This post will display how to create a barplot in RStudio. In this example we will look at homerun distribution for the year of 1980. First you have to install the Lahman, sqldf, and ggplot2 packages. Next bring them in by doing the following:

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

###Extracting the Data

Next, we need to extract the data that we would like to be in our plot by creating the query below:

```{r}
query<-"SELECT name,HR
FROM Teams
WHERE yearID=1980
ORDER BY HR"

result<-sqldf(query)

result$name<-factor(result$name,levels=result$name)
```

###Visualizing the Data

Finally, we can create the plot by using the following commands:

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity',color="blue",fill="white")+
  coord_flip()+
  ylab("homeruns")+
  xlab("team")+
  ggtitle("1980 Team Homerun Distribution")
```

