---
title: Scatterplots
author: Katie Reisinger
date: '2017-10-17'
slug: scatterplots
categories:
  - ploting data
  - data visualization
  - R
tags:
  - R Markdown
  - plot
---

This post is a tutorial on how to use data visualization in RStudio to create a scatter plot. First you have to install the Lahman, sqldf, and ggplot2 packages. Next bring them in by doing the following:

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

###Extracting the Data

Next, we need to extract the data that we would like to be in our plot by creating the query below:

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP by playerID
HAVING sum(HR)>=400"

result<-sqldf(query)
```

###Visualizing the Data

Finally, we can create the plot by using the following commands:

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")+
  ggtitle("Career Strikeouts VS Homeruns for Great Hitters")+
  xlab("career strikeouts")+
  ylab("career homeruns")
```

